Efficient implementation of kernel filtering

### 2007-07-02 article/Article.tex
add a template for the graphics
darcs-hash:20070702195110-2fc9d-680007fd7ceb06e19cb5b764d92163ce162569d6.gz

>>>>

\begin{figure}[htbp]
\begin{center}
\subfigure[Dilation]{\includegraphics[scale=0.62]{consolidatedMorphology-perf2D-dilation-small}}
\subfigure[Opening]{\includegraphics[scale=0.62]{consolidatedMorphology-perf2D-opening-small}}
\subfigure[Gradient]{\includegraphics[scale=0.62]{consolidatedMorphology-perf2D-gradient-small}}
\subfigure[TODO]{\includegraphics[scale=0.62]{consolidatedMorphology-perf2D-gradient-small}}
\subfigure[TODO]{\includegraphics[scale=0.62]{consolidatedMorphology-perf2D-gradient-small}}
\subfigure[TODO]{\includegraphics[scale=0.62]{consolidatedMorphology-perf2D-gradient-small}}
\caption{TODO}
\end{center}
\end{figure}
